\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-04-28 forwards-and-backwards.tex
alison edits

For the second claim, first define $\tau(t) = T(t)-t$.
Since if $\tau(t) \ge -(\epsilon^2 + t)/2$,
then $1/(\epsilon^2 + T(t)) \le 2/(\epsilon^2 + t)$,
while $\epsilon^2 + T(t) \ge \epsilon^2$ always,
partitioning over
$\{ \tau(t) \ge -(\epsilon^2 + t)/2 \}$ and its complement,
\begin{align}
   \| \psi^{\epsilon,x} \|_\infty
    &=
        \IE\left[ 
            \frac{1}{\big(2 \pi (\epsilon^2+T(t))\big)^{d/2}}
        \right] \nonumber
    \\ & \le
        \frac{C}{(\epsilon^2 + t)^{d/2}}
        + 
        \frac{C}{\epsilon^d}
        \IP\left\{
            \tau(t) < - (\epsilon^2 + t) / 2
        \right\}. \label{eqn:psi_infty_bound}
\end{align}
Now, observe that since $\IE[e^{-\Pi(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
by Markov's inequality,
\begin{align}
    \IP\left\{
        \tau(t) < - \frac{\epsilon^2 + t}{2}
    \right\}
    &=
    \IP\left\{
        e^{-\Pi(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
    \right\}
\nonumber
\\
&\leq \frac{\IE[\exp\big(-\Pi(\theta t)\big)]}{\exp\big(-\theta(t-\epsilon^2)/2\big)}
\nonumber
    \\&=
    \frac{
        \exp(- \theta t(1 - e^{-1}))
    }{
        \exp(- \theta (t - \epsilon^2) / 2)
    }
\nonumber
    \\&=
    \exp\left\{ - \chi \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
\label{bound for negative tau}
\end{align}
where $\chi = 1/2 - e^{-1} > 0$.
The second term in \eqref{eqn:psi_infty_bound} is therefore bounded by
\[
    C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\chi \theta t - \epsilon^2 \theta / 2}
    \frac{1}{(\epsilon^2 + t)^{d/2}} .
\]
Now observe that the derivative (with respect to $t$) of 
$e^{-\chi \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ 
is
\[
    \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \chi \theta \right)
    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\chi \theta t - \epsilon^2 \theta / 2} ,
\]
which is negative if $\theta(\epsilon^2 + t) > d/2 \chi$.
At the maximum, $(\epsilon^2 + t) = d / (2\chi \theta)$,
so $(1 + t/\epsilon^2) = d /(2\chi \theta \epsilon^2)$,
and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$
(since we've assumed that $\theta \epsilon^2$ is bounded below).
Therefore, the second term in \eqref{eqn:psi_infty_bound} 
is bounded by $C / (\epsilon^2 + t)^{d/2}$
(for a different constant $C$).
Substituting this into \eqref{eqn:psi_infty_bound} yields the result.
\end{proof}
\comment{ALISON: Actually the last calculation gives a much better bound which we will
need later. I'll sort this out tomorrow.}

@@

\begin{lemma}
    \label{Lemma:BoundPsiHS2}
    In the notation of Lemma~\ref{PsiBoundHS},
    %and with $A$ as in Lemma~\ref{lem:poisson_ld},
    \begin{multline}
\label{heat kernel estimate}
        \left|
            \psi_t^{\epsilon, x}(y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        \\
\le
        \frac{C}{(\epsilon^2 \theta)^{d/2}}
        p_{6(\epsilon^2+t)}(x, y)
        +
	    C \left(1+
	    \frac{1}{(\epsilon^2 + t)^{d/2}}\right)
	    \exp(- \epsilon^2 \theta / 2)
        %+
        %\frac{C}{(\epsilon^2 + t)^{d/2}}
        %\IP\left\{
        %    \tau(t) > A(\epsilon^2 + t)
        %\right\} 
	    .
    \end{multline}
\end{lemma}

\begin{proof}
    Still using the notation of Lemma~\ref{PsiBoundHS},
%the three terms on the right hand side of 
%equation~(\ref{heat kernel estimate})
%    correspond to bounds obtained by partitioning
 we partition into three events according to the value of $\tau(t)$.
    Let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
    $A_2 = \{ \tau(t) > 2(\epsilon^2 + t) \}$,
    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le 2(\epsilon^2 + t) \}$.
    Then,
    \begin{align*}
        \left|
            \psi_t^{\epsilon, x}(y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left|
        \IE\left[
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right]
        \right|
        \\&\le
        \IE\left[
            (1_{A_1} + 1_{A_2} + 1_{A_3})
            \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        \right] .
    \end{align*}
    For the first term, note that if $a < b$ then
    \begin{align*}
        |p_a(x, y) - p_b(x, y)| 
        &=
        \frac{1}{(2\pi)^{d/2}}
        \left|
            \frac{1}{a^{d/2}}
            e^{-\|x - y\|^2 / 2a}
            -
            \frac{1}{b^{d/2}}
            e^{-\|x - y\|^2 / 2b}
        \right|
        \\ &=
        \frac{1}{(2\pi a^2)^{d/2}}
            e^{-\|x - y\|^2 / 2b}
        \left|
            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
            -
            \left(\frac{a}{b}\right)^{d/2}
        \right|
        \\ &\le
        C \left(\frac{b}{a}\right)^{d/2}
        p_b(x, y) ,
    \end{align*}
    where the inequality follows because both terms under the absolute value 
are less than 1.
Since, on the event $A_1$, $\tau(t)<0$, we can  
apply this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
and, using the bound~(\ref{bound for negative tau}),
\comment{ALISON: It's actually using the bound derived just below (7.4) which is 
much stronger than stated there}
    \begin{align*}
        \IE\left[
            1_{A_1} |p_a(x, y) - p_b(x, y)| 
        \right]
        & \le
            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
            p_{\epsilon^2 + t}(x, y) 
            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
        \\ & \le
            C \frac{1}{\epsilon^d}
            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
        \\ & \le
        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
    \end{align*}

    For the third term, we will first collect some facts.
    Observe that on the event $A_3$,
    $\epsilon^2 + t + \tau(t)$ is between
    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t))$,
    and for any $s$ in this interval,
    \begin{align}
        p_{2s}(y)
        &\le \nonumber
        \left( \frac{
            2 (\epsilon^2 + t)3
        }{
            \epsilon^2 + t
        } \right)^{d/2}
        p_{6(\epsilon^2 + t)}(x, y)
        \\ &= \label{eqn:p_bounded_on_interval}
        6^{d/2}
        p_{6(\epsilon^2 + t)}(x, y) .
    \end{align}
    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
    \begin{align}
        \frac{\|x - y\|^2}{s} p_s(x, y)
        &= \nonumber
        \frac{4}{(2 \pi s)^{d/2}}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \frac{\|x-y\|^2}{4s}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \\ &\le \label{eqn:p_deriv_term2}
        C p_{2s}(x, y) .
    \end{align}
    Now, by the Intermediate Value Theorem,
    \begin{align}
\label{deduction from IVT}
        \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left| \tau(t) \right|
        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
    \end{align}
    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
   Since 
    \begin{align*}
        \partial_ s p_s(x, y)
        &=
        \partial_s
        \left(
            \frac{1}{(2 \pi s)^{d/2}}
            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
        \right)
        \\ &=
        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
    \end{align*}
    applying the inequality~\eqref{eqn:p_deriv_term2},
    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
    and then \eqref{eqn:p_bounded_on_interval},
    we have that for any $s \in ((\epsilon^2 + t)/ 2, 3(\epsilon^2 + t))$,
    \begin{align*}
        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
        \le
        \frac{C}{s} p_{2s}(x, y) 
        \le
        \frac{C}{\epsilon^2 + t} p_{6(\epsilon^2 + t)}(x, y) .
    \end{align*}
    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
into~(\ref{deduction from IVT}),
    \begin{align*}
        \IE\left[
            1_{A_3}
            \left|
                p_{\epsilon^2 + t + \tau(t)}(x, y)
                -
                p_{\epsilon^2 + t}(x, y)
            \right|
        \right]
        &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[|\tau(t)|\right]
        \\ &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[\tau(t)^2\right]^{1/2}
        \\ &=
            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
                p_{6(\epsilon^2 + t)}(x, y)
        \\ &\le
            \frac{C}{\sqrt{\theta \epsilon^2}}
                p_{6(\epsilon^2 + t)}(x, y) ,
    \end{align*}
    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.

@@

We now have the ingredients that we need to write down a continuity 
estimate for $\rho_\epsilon*\eta$.
We fix $\delta>0$ and 
suppose that $s>\delta$.
Let us write
\[
\widehat{\epsilon}(\delta,\epsilon,\theta):=
e^{-\epsilon^2\theta/2}\left(1+\frac{1}{(\epsilon^2+\delta)^{d/2}}\right),
%\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
\]
and note that under the assumption that $\epsilon^2\theta\to \infty$, for 
each fixed $\delta>0$,  
$\lim_{\epsilon\to 0, \theta\to\infty}
\widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
and Lemma~\ref{Lemma:BoundPsiHS2},
we have
\begin{align}
& |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \nonumber 
= |\langle p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z),\eta_s(dz) \rangle | 
\nonumber
\\ 
&\qquad
    \leq 
\big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
\eta_0(dz)\big\rangle 
\nonumber
	\\ &\qquad \qquad {}
    +
\int_0^{s-\delta}
\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)| 
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
    \\ &\qquad \qquad {}
	+ \frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z), \eta_0(dz)
\big\rangle
	+\widehat{\epsilon}(\delta,\epsilon,\theta)\langle 1,\eta_0(dz)\rangle
	\nonumber
    \\ &\qquad \qquad {}
+ \int_{s-\delta}^s \big\langle 
|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
    \\ &\qquad \qquad {}
    +
\frac{C}{(\epsilon^2\theta)^{d/2}}
\int_0^{s-\delta}
\big\langle |p_{6(s-r+\epsilon^2)}(y,z)+
p_{6(s-r+\epsilon^2)}(w,z)|
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
\\ & \qquad \qquad {}
+ |M_s(y)|+|M_s(w)| 
%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
%\big)  
\nonumber
\\ & \qquad 
\leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
\big(p_{2(s+\epsilon^2}(y,z)+p_{2(s+\epsilon^2}(w,z)\big),\eta_0(dz)\Big\rangle
\nonumber
\\ & \qquad \qquad  {}
+
\int_0^{s-\delta}\Big\langle\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
\big(p_{2(s-t+\epsilon^2}(y,z)+p_{2(s-r+\epsilon^2}(w,z)\big)
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz)\Big\rangle dr
\nonumber
\\ & \qquad \qquad  {}
	+ \big\langle \frac{C}{(\theta\epsilon^2)^{d/2}}\Big( 
	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
	\widehat{\epsilon}(\delta,\epsilon,\theta) , \eta_0(dz)
\big\rangle
\nonumber
\\ & \qquad \qquad  {}
+
\int_0^{s-\delta}
\big\langle \Big\{
\frac{C}{(\epsilon^2\theta)^{d/2}}
|p_{6(s-r+\epsilon^2)}(y,z)+
p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
\\ & \qquad \qquad  {}
+ |M_s(y)|+|M_s(w)|. 
%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
%\big) . 
\label{difference in rhos}
\end{align} 
\comment{MISSING A TERM? the $\int_{s-\delta}^s$ one; and say it's bounded because of the moment bounds}
Although this expression is lengthy, we have successfully isolated the
terms involving $\|y-w\|$, which will control the regularity as we pass to the
limit. Asymptotically, we 
don't expect the martingale terms to contribute, since their 
quadratic variation scales with $\theta/(N\epsilon^d)$, and
under the assumption that $\epsilon^2\theta\to\infty$,
for any fixed $\delta>0$, if $s > \delta$ the terms arising from 
approximating the transition 
density of the Gaussian 
walk by the heat kernel at a fixed time, will tend to zero. 
There is some technical work to be done to rigorously identify the
limit points of $\rho_\epsilon*\eta^N$, but 
it really amounts to 
applying the tower property and our moment bounds from 
Lemma~\ref{bounds on moments} and 
Corollary~\ref{alternative form moment bounds}.

>>>>

For the second claim, first define $\tau(t) = T(t)-t$.
Since if $\tau(t) \ge -(\epsilon^2 + t)/2$,
then $1/(\epsilon^2 + T(t)) \le 2/(\epsilon^2 + t)$,
while $\epsilon^2 + T(t) \ge \epsilon^2$ always,
partitioning over
$\{ \tau(t) \ge -(\epsilon^2 + t)/2 \}$ and its complement,
\begin{align}
   \| \psi^{\epsilon,x} \|_\infty
    &=
        \IE\left[ 
            \frac{1}{\big(2 \pi (\epsilon^2+T(t))\big)^{d/2}}
        \right] \nonumber
    \\ & \le
        \frac{C}{(\epsilon^2 + t)^{d/2}}
        + 
        \frac{C}{\epsilon^d}
        \IP\left\{
            \tau(t) < - (\epsilon^2 + t) / 2
        \right\}. \label{eqn:psi_infty_bound}
\end{align}
Now, observe that since $\IE[e^{-\Pi(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
by Markov's inequality,
\begin{align}
    \IP\left\{
        \tau(t) < - \frac{\epsilon^2 + t}{2}
    \right\}
    &=
    \IP\left\{
        e^{-\Pi(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
    \right\}
\nonumber
\\
&\leq \frac{\IE[\exp\big(-\Pi(\theta t)\big)]}{\exp\big(-\theta(t-\epsilon^2)/2\big)}
\nonumber
    \\&=
    \frac{
        \exp(- \theta t(1 - e^{-1}))
    }{
        \exp(- \theta (t - \epsilon^2) / 2)
    }
\nonumber
    \\&=
    \exp\left\{ - \chi \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
\label{bound for negative tau}
\end{align}
where $\chi = 1/2 - e^{-1} > 0$.
The second term in \eqref{eqn:psi_infty_bound} is therefore bounded by
\[
	C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\chi \theta t }%- \epsilon^2 \theta / 2}
	\frac{1}{(\epsilon^2 + t)^{d/2}}e^{-\epsilon^2 \theta/2} .
\]
Now observe that the derivative (with respect to $t$) of 
	$e^{-\chi \theta t} % - \epsilon^2 \theta / 2} 
	(1 + t/\epsilon^2)^{d/2}$ 
is
\[
    \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \chi \theta \right)
    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\chi \theta t },%- \epsilon^2 \theta / 2} ,
\]
which is negative if $\theta(\epsilon^2 + t) > d/2 \chi$.
At the maximum, %$(1+\epsilon^2/t) = d / (2\chi \epsilon^2\theta)$, so
$(1 + t/\epsilon^2) = d /(2\chi \theta \epsilon^2)$,
and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$
(since we've assumed that $\theta \epsilon^2$ is bounded below).
Therefore, 
we have the bound
\begin{equation}
	\label{small tau bound}
	\frac{1}{\epsilon^d}
        \IP\left\{
            \tau(t) < - (\epsilon^2 + t) / 2
        \right\}
\leq \frac{C}{(\epsilon^2 + t)^{d/2}} e^{-\epsilon^2\theta/2}.
\end{equation}
%(for a different constant $C$).
Substituting this into \eqref{eqn:psi_infty_bound} yields the result.
\end{proof}

@@

\begin{lemma}
    \label{Lemma:BoundPsiHS2}
    In the notation of Lemma~\ref{PsiBoundHS},
    %and with $A$ as in Lemma~\ref{lem:poisson_ld},
	\begin{equation}
\label{heat kernel estimate}
        \left|
            \psi_t^{\epsilon, x}(y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        %\\
\le
        \frac{C}{(\epsilon^2 \theta)^{1/2}}
        p_{6(\epsilon^2+t)}(x, y)
        +
	    \frac{C}{(\epsilon^2 + t)^{d/2}}
	    \exp(- \epsilon^2 \theta / 2)
        %+
        %\frac{C}{(\epsilon^2 + t)^{d/2}}
        %\IP\left\{
        %    \tau(t) > A(\epsilon^2 + t)
        %\right\} 
	    .
	\end{equation}
\end{lemma}

\begin{proof}
    Still using the notation of Lemma~\ref{PsiBoundHS},
%the three terms on the right hand side of 
%equation~(\ref{heat kernel estimate})
%    correspond to bounds obtained by partitioning
 we partition into three events according to the value of $\tau(t)$.
    Let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
    $A_2 = \{ \tau(t) > 2(\epsilon^2 + t) \}$,
    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le 2(\epsilon^2 + t) \}$.
    Then,
    \begin{align*}
        \left|
            \psi_t^{\epsilon, x}(y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left|
        \IE\left[
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right]
        \right|
        \\&\le
        \IE\left[
            (1_{A_1} + 1_{A_2} + 1_{A_3})
            \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        \right] .
    \end{align*}
    For the first term, note that if $a < b$ then
    \begin{align*}
        |p_a(x, y) - p_b(x, y)| 
        &=
        \frac{1}{(2\pi)^{d/2}}
        \left|
            \frac{1}{a^{d/2}}
            e^{-\|x - y\|^2 / 2a}
            -
            \frac{1}{b^{d/2}}
            e^{-\|x - y\|^2 / 2b}
        \right|
        \\ &=
        \frac{1}{(2\pi a^2)^{d/2}}
            e^{-\|x - y\|^2 / 2b}
        \left|
            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
            -
            \left(\frac{a}{b}\right)^{d/2}
        \right|
        \\ &\le
        C \left(\frac{b}{a}\right)^{d/2}
        p_b(x, y) ,
    \end{align*}
    where the inequality follows because both terms under the absolute value 
are less than 1.
Since, on the event $A_1$, $\tau(t)<0$, we can  
apply this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
and, using the bound~(\ref{bound for negative tau}),
    \begin{align*}
        \IE\left[
            1_{A_1} |p_a(x, y) - p_b(x, y)| 
        \right]
        & \le
            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
            p_{\epsilon^2 + t}(x, y) 
            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
        \\ & \le
            C \frac{1}{\epsilon^d}
            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
        \\ & \le
	    \frac{C}{(\epsilon^2+t)^{d/2}} \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
    \end{align*}

    For the third term, we will first collect some facts.
    Observe that on the event $A_3$,
    $\epsilon^2 + t + \tau(t)$ is between
    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t)$,
    and for any $s$ in this interval,
    \begin{align}
        p_{2s}(y)
        &\le \nonumber
        \left( \frac{
            2 (\epsilon^2 + t)3
        }{
            \epsilon^2 + t
        } \right)^{d/2}
        p_{6(\epsilon^2 + t)}(x, y)
        \\ &= \label{eqn:p_bounded_on_interval}
        6^{d/2}
        p_{6(\epsilon^2 + t)}(x, y) .
    \end{align}
    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
    \begin{align}
        \frac{\|x - y\|^2}{s} p_s(x, y)
        &= \nonumber
        \frac{4}{(2 \pi s)^{d/2}}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \frac{\|x-y\|^2}{4s}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \\ &\le \label{eqn:p_deriv_term2}
        C p_{2s}(x, y) .
    \end{align}
    Now, by the Intermediate Value Theorem,
    \begin{align}
\label{deduction from IVT}
        \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left| \tau(t) \right|
        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
    \end{align}
    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
   Since 
    \begin{align*}
        \partial_ s p_s(x, y)
        &=
        \partial_s
        \left(
            \frac{1}{(2 \pi s)^{d/2}}
            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
        \right)
        \\ &=
        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
    \end{align*}
    applying the inequality~\eqref{eqn:p_deriv_term2},
    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
    and then \eqref{eqn:p_bounded_on_interval},
    we have that for any $s \in ((\epsilon^2 + t)/ 2, 3(\epsilon^2 + t))$,
    \begin{align*}
        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
        \le
        \frac{C}{s} p_{2s}(x, y) 
        \le
        \frac{C}{\epsilon^2 + t} p_{6(\epsilon^2 + t)}(x, y) .
    \end{align*}
    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
into~(\ref{deduction from IVT}),
    \begin{align*}
        \IE\left[
            1_{A_3}
            \left|
                p_{\epsilon^2 + t + \tau(t)}(x, y)
                -
                p_{\epsilon^2 + t}(x, y)
            \right|
        \right]
        &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[|\tau(t)|\right]
        \\ &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[\tau(t)^2\right]^{1/2}
        \\ &=
            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
                p_{6(\epsilon^2 + t)}(x, y)
        \\ &\le
            \frac{C}{\sqrt{\theta \epsilon^2}}
                p_{6(\epsilon^2 + t)}(x, y) ,
    \end{align*}
    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.

@@

We now have the ingredients that we need to write down a continuity 
estimate for $\rho_\epsilon*\eta$.
We fix $\delta>0$ and 
suppose that $s>\delta$.
Let us write
\[
\widehat{\epsilon}(\delta,\epsilon,\theta):=
\frac{1}{(\epsilon^2+\delta)^{d/2}}
e^{-\epsilon^2\theta/2}, %\left(1+\frac{1}{(\epsilon^2+\delta)^{d/2}}\right),
%\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
\]
and note that under the assumption that $\epsilon^2\theta\to \infty$, for 
each fixed $\delta>0$,  
$\lim_{\epsilon\to 0, \theta\to\infty}
\widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
and Lemma~\ref{Lemma:BoundPsiHS2},
we have
\begin{align}
& |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \nonumber 
= |\langle p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z),\eta_s(dz) \rangle | 
\nonumber
\\ 
&\qquad
    \leq 
\big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
\eta_0(dz)\big\rangle 
\nonumber
	\\ &\qquad \qquad {}
    +
\int_0^{s-\delta}
\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)| 
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
    \\ &\qquad \qquad {}
	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(%\big\langle 
	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big) %, \eta_0(dz)
%\big\rangle
	+\widehat{\epsilon}(\delta,\epsilon,\theta) %\langle 1
	,\eta_0(dz)\rangle
	\nonumber
    \\ &\qquad \qquad {}
    +
\int_0^{s-\delta}
\big\langle \Big\{
\frac{C}{(\epsilon^2\theta)^{1/2}}
|p_{6(s-r+\epsilon^2)}(y,z)+
p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
    %\frac{C}{(\epsilon^2\theta)^{1/2}}
%\int_0^{s-\delta}
%\big\langle |p_{6(s-r+\epsilon^2)}(y,z)+
%p_{6(s-r+\epsilon^2)}(w,z)|
%\cdot |F(\rho_\epsilon*\eta_r(z)|, 
%\eta_r(dz) \big\rangle  dr
%\nonumber
    \\ &\qquad \qquad {}
+ \int_{s-\delta}^s \big\langle 
|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
\\ & \qquad \qquad {}
+ |M_s(y)|+|M_s(w)| 
%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
%\big)  
\nonumber
\\ & \qquad 
\leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
\big(p_{2(s+\epsilon^2}(y,z)+p_{2(s+\epsilon^2}(w,z)\big),\eta_0(dz)\Big\rangle
\nonumber
\\ & \qquad \qquad  {}
+
\int_0^{s-\delta}\Big\langle\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
\big(p_{2(s-t+\epsilon^2}(y,z)+p_{2(s-r+\epsilon^2}(w,z)\big)
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz)\Big\rangle dr
\nonumber
\\ & \qquad \qquad  {}
	+ \big\langle \frac{C}{(\theta\epsilon^2)^{1/2}}\Big( 
	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
	\widehat{\epsilon}(\delta,\epsilon,\theta) , \eta_0(dz)
\big\rangle
\nonumber
\\ & \qquad \qquad  {}
+
\int_0^{s-\delta}
\big\langle \Big\{
\frac{C}{(\epsilon^2\theta)^{1/2}}
|p_{6(s-r+\epsilon^2)}(y,z)+
p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
    \\ &\qquad \qquad {}
+ \int_{s-\delta}^s \big\langle 
|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
\cdot |F(\rho_\epsilon*\eta_r(z)|, 
\eta_r(dz) \big\rangle  dr
\nonumber
\\ & \qquad \qquad  {}
+ |M_s(y)|+|M_s(w)|. 
%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
%\big) . 
\label{difference in rhos}
\end{align} 
Although this expression is lengthy, we have successfully isolated the
terms involving $\|y-w\|$, which will control the regularity as we pass to the
limit. Asymptotically, we 
don't expect the martingale terms to contribute, since their 
quadratic variation scales with $\theta/(N\epsilon^d)$; % and
under the assumption that $\epsilon^2\theta\to\infty$,
for any fixed $\delta>0$, %if $s > \delta$ 
the terms arising from 
approximating the transition 
density $\psi_{s-r}^{\epsilon, \cdot}(\cdot)$ of the Gaussian 
walk by $p_{s-r+\epsilon^2}(\cdot,\cdot)$ at times 
with $s-r>\delta$ will tend to zero; and  
the moment bounds of Lemma~\ref{bounds on moments} 
will allow us to control the integral over $[s-\delta, s]$.
There is some technical work to be done to rigorously identify the
limit points of $\rho_\epsilon*\eta^N$, but 
it really amounts to 
applying the tower property and our moment bounds from 
Lemma~\ref{bounds on moments} and 
Corollary~\ref{alternative form moment bounds}.
